---
title       : How To Use The China/Latin America GDP Correlation Shiny App
subtitle    : 
author      : Boyd Ingalls
job         : Analyst
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---



## China Becomes An Increasingly Important Driver of World Commodity Demand and Pricing




China has gained a growing proportion of the world's manufacturing capacity over the last several decades producing an ever larger fraction of the world's supply of manufactured goods. As a result China has become a much larger consumer of commodities and raw materials with increased influence on commodity demand and pricing.
(All data in this presentation is from the World Bank here: http://data.worldbank.org/indicator/NY.GDP.MKTP.CD)

---

```{r echo = F, warning = F, message = F}
require(ggplot2); require(scales)
data1 <- read.csv("CHNGPERCGDPData.csv", header = TRUE)
p <- ggplot(data1, aes(Year, Perc_GDP)) + geom_point(size = 3, color = "darkred") + geom_line() + ylab("China Percentage of World GDP") + theme(panel.background = element_rect(fill = "#E5F5F9")) + scale_y_continuous(labels=percent)
print(p)
```

In 1990 China's share of world GDP was around 2%. By 2015 it had grown to almost 15%.

---

Latin American economies have long relied heavily on commodity exports, from Spanish colonial shipments of precious metals to 
current exports of oil, copper, and agricultural products. To the degree that Latin American economies lean on exports they are vulnerable to changes in demand, and ultimately Chinese consumption of commodities and the effects of Chinese demand on prices.

The China/Latin America GDP Correlation Shiny App is a data visualization tool that allows the user to get a visual sense of how closely certain key Latin American economies are tied to China's.

---

```{r echo = F}
data3 <- read.csv("WB_GDP_Chile.csv", header = TRUE)

d <- ggplot(data3, aes(Chile, China, size = 3, colour = "blue")) + geom_point(colour = "#33a02c", shape = 17) + labs(title = "Selected Correlations\nChile", x = "China GDP in $ Millions", y = "Comparison GDP in $ Milliions") + theme(plot.title = element_text(face = "bold", size = 20)) + theme(axis.title = element_text(face = "bold", size = 16)) + scale_x_continuous(labels = comma) + scale_y_continuous(labels = comma) + theme(panel.background = element_rect(fill = "#E5F5F9")) + geom_smooth(method = lm, size = 1, se = FALSE, colour = "#33a02c") + theme(legend.position = "none")
print(d)
```


The chart above illustrates Chile's GDP correlated with China. The data points cluster closely around the regression line indicating a strong correlation between the two GDPs.

---

The China/Latin America GDP Correlation Shiny App allows the user to pick any of the following countries and add them to the plot:

1. Argentina
2. Brazil
3. Chile
4. Mexico
5. Peru

The user can view the plots seperately or compare countries by checking and unchecking their boxes.

